---
title: "GEOG-533 Lab 9"
author: "Deborah Gabay"
output:
  html_notebook:
    toc: yes
    toc_float: yes
  html_document:
    df_print: paged
    toc: yes
---

## Question 1
Use R package **UScensus2010county** to complete the following tasks:  (20 pt.)

### Question 1(a)
Plot a map of New York counties using the **plot** function.
```{r}
library(rgdal)
if (!require(UScensus2010county)) {install.county("osx")}
if (!require(UScensus2010tract)) {install.tract("osx")}
library(UScensus2010)
library(UScensus2010county)
data(new_york.county10)
shp <- new_york.county10
plot(shp)
```

### Question 1(b)	
Plot a map of New York counties using the **qtm** function.
```{r}
library(tmap)
qtm(shp)
```


### Question 1(c)	
How many counties in New York State?
```{r}
nrow(shp)
## There are 62 counties in New York State
```

### Question 1(d)	
What’s the 3-digit **fips** code of Broome County?
```{r}
df <- shp@data
df
## The FIPS code of Broome County is 007
```

### Question 1(e)	
Compute descriptive statistics of the population column (**P0010001**), including total, minimum, maximum, mean, median, and skewness. 
```{r}
sum(df$P0010001)
min(df$P0010001)
max(df$P0010001)
mean(df$P0010001)
median(df$P0010001)
library(moments)
skewness(df$P0010001)

## There is a total population of 19378102. The minimum population of all the counties is 4836, the maximum is 2504700, the mean is 312550, the median is 91301, and the skewness is 2.579801.
```

### Question 1(f)	
Create a histogram and a boxplot of the population.
```{r}
Population <- df$P0010001
hist(Population)
boxplot(Population)
```


## Question 2
Use R package **UScensus2010tract** to complete the following tasks:    (20 pt.)
```{r}
library(UScensus2010tract)
```

### Question 2(a)	
Plot a map of New York census tracts using the **plot** function.
```{r}
data(new_york.tract10)
shp <- new_york.tract10
plot(shp)
```

### Question 2(b)
Compute the total population based on census tracts.
```{r}
df <- shp@data
df
sum(df$P0010001)
## The total population based on census tracts is 19378102
```

### Question 2(c)
Select all census tracts in Broome County and plot the map. 
```{r}
sel <- df$county == "007"
plot(shp[sel,])
```

### Question 2(d)
What’s the total population of Broome County?
```{r}
sum(df$P0010001[df$county == "007"])
## The total population of Broome County is 200600
```

### Question 2(e)
Create a histogram and a boxplot of population based on census tracts of Broome County.
```{r}
broome_county_population <- (df$P0010001[df$county == "007"])
hist(broome_county_population)
boxplot(broome_county_population)
```

### Question 2(f)
Select the first five columns of the shapefile of Broome County census tract; add a new population ratio column (= census tract population / county population); save the new shapefile to the hard drive. 
```{r}
broome_county_shp <- subset(shp, county == "007")
broome_county_tracts <- broome_county_shp[, 1:5]
broome_county_tracts$PopulationRatio <- (broome_county_tracts$P0010001 / 200600)
```


## Question 3

Use R packages **raster** and **ncdf4** to complete the following tasks:     (20 pt.)
```{r}
library(raster)
library(ncdf4)
```

### Question 3(a)		
Load the multi-band raster dataset “NDVI.nc” into R.
```{r}
setwd("~/Desktop/533/Blank Labs/Lab_09")
ndvi.rb <- brick("NDVI.nc")
```

### Question 3(b)		
Get the basic information about the dataset, including the number of rows, columns, cells, and bands; spatial resolution, extent, bounding box, and projection.
```{r}
ndvi.rb
```

### Question 3(c)	
Aggregate all bands to generate a mean NDVI raster and a maximum NDVI raster; save the two new raster datasets to the hard drive. 
```{r}
aggregate(ndvi.rb)
mean(ndvi.rb)
max(ndvi.rb)
```

### Question 3(d)			
Plot the maps of monthly NDVI of the year 2001
```{r}
ndvi2001 <- ndvi.rb[[13:24]]
plot(ndvi2001)
```

### Question 3(e)	
Create histograms of monthly NDVI of the year 2001.
```{r}
hist(ndvi2001, 1)
hist(ndvi2001, 2)
hist(ndvi2001, 3)
hist(ndvi2001, 4)
hist(ndvi2001, 5)
hist(ndvi2001, 6)
hist(ndvi2001, 7)
hist(ndvi2001, 8)
hist(ndvi2001, 9)
hist(ndvi2001, 10)
hist(ndvi2001, 11)
hist(ndvi2001, 12)
```

### Question 3(f)			
Plot the NDVI map of July 2000; click any location with data on the map and retrieve the NDVI time series for all years; plot the NDVI time series of the selected location. 
```{r}
hist(ndvi2001, 7)
values <- ndvi2001[50,50]
plot(as.vector(values), type = "b")
```

